### 2015-05-15 evaluation.tex
added url in tool link
some fixes

\begin{table*}[t]
\small
\centering
\setlength{\tabcolsep}{0.45em}
\caption{Comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l r rrrr rrrr rrrr}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\vspace{-3mm}
\end{table*}

@@

@@

Most of the races that \whoop and \corral discovered can be classified in two cases. The first case is accessing a global counter (or flag) from concurrent entry points, without a lock. This might be for performance, and indeed a lot of the races we found might be benign. Even benign races, though, lead to undefined behavior according to the C standard, and it is well known that undefined behaviors can lead to unexpected results when combined with aggressive compiler optimizations. The second case is an entry point modifying a field of a struct (either global or passed as a parameter) without a lock. This can lead to a race if another entry point simultaneously accesses the same field of the same struct.

>>>>

\begin{table*}[t]
\small
\centering
\setlength{\tabcolsep}{0.4em}
\caption{Comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l r rrrr rrrr rrrr}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\vspace{-3mm}
\end{table*}

@@

For reproducibility, we make all of our tools (including source) and benchmarks available online:

\begin{scriptsize}
\textbf{\texttt{\url{http://multicore.doc.ic.ac.uk/tools/Whoop/ASE2015}}}
\end{scriptsize}

@@

Most of the races that \whoop and \corral discovered can be classified in two cases. The first case is accessing a global counter (or flag) from concurrent entry points, without holding a lock. This might be for performance, and indeed a lot of the races we found might be benign. Even benign races, though, lead to undefined behavior according to the C standard, and it is well known that undefined behaviors can lead to unexpected results when combined with aggressive compiler optimizations. The second case is an entry point modifying a field of a struct (either global or passed as a parameter) without holding a lock. This can lead to a race if another entry point simultaneously accesses the same field of the same struct.
